Live and Let Die? (Delayed Issues not Harder to Resolve)

### 2015-08-02 phaseDelay.tex
Updates from ShareLaTeX

In this paper, we have examined contemporary project data for traces of
the widely-believed delayed issue effect.
We found that, in the literature, the evidence for this effect was very spare--
in fact, we found
%and (in a $21^{st}$).  %don't know what this is supposed to be
We suspect that a very old result was requoted, without being 
critically re-examined, for literally decades.

@@

One hypothesized explanation that can be ruled out is that this lack of
a phase delay effect is due to the use of TSP.
  To the contrary, four non-TSP  case studies reported that the expected exponential growth in cost-to-fix was not observed:

>>>>

In this paper, we have examined contemporary project data for traces of
the widely-believed delayed issue effect.
We found that, in the literature, the evidence for this effect was very spare--
in fact, we found
just as many articles supporting this  exponential effect~\cite{Boehm76,Boehm81,teck,Fagan76,Stephenson76}
than otherwise~\cite{Clutterbuck09,Clutterbuck09,Boehm80} and one paper that
offered evidence consistent with {\em both}
the the delayed issue effect and its opposite~\cite{shull02}.

@@
